### 2021-04-08 papers/SYRCoSE/related.tex
TODO
Related work: typos / grammar

Event structures were introduced by Winskel to study the semantics of 
calculus of communicating systems~\cite{Winskel:82}. 
Several modification of event structures~\cite{Langerak:91, Boudol-Castellani:1991}
were later proposed to tackle similar problems.  
To the best of our knowledge, there were no attempts 
to mechanise the classical theory of event structures 
in proof assistants.

>>>>

\todo{Fix Winskel1986 vs Winskel 1982 (introduction vs related work)}

Event structures were introduced by Winskel to study the semantics of 
the calculus of communicating systems~\cite{Winskel:82}. 
Several modifications of event structures~\cite{Langerak:91, Boudol-Castellani:1991}
were later proposed to tackle similar problems.  
To the best of our knowledge, there were no attempts 
to mechanise the classical theory of event structures 
in proof assistants.
